Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2015-07-01 Paper/paper.tex
new plots

\textbf{With BH-BH Templates}

@@

\textbf{With NS-BH Templates}

@@

	\textbf{With BH-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TN_chirpMassCIWidth90_vs_SNR_q23.pdf}\\ 
	\textbf{With NS-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TT_chirpMassCIWidth90_vs_SNR_q23.pdf}%\quad

@@

\textbf{With BH-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TN_EtaBias_vs_SNR_q23.pdf}\\ 
\textbf{With NS-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TT_EtaBias_vs_SNR_q23.pdf}%\quad

@@

	\textbf{With BH-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TN_EtaCIWidth90_vs_SNR_q23.pdf}\\ 
	\textbf{With NS-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TT_EtaCIWidth90_vs_SNR_q23.pdf}%\quad

@@

		of the dimensionless

@@

\textbf{With BH-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TN_BHspinBias_vs_SNR_q23.pdf}\\ 
\textbf{With NS-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TT_BHspinBias_vs_SNR_q23.pdf}%\quad

@@

	\textbf{With BH-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TN_BHspinCIWidth90_vs_SNR_q23.pdf}\\ 
	\textbf{With NS-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TT_BHspinCIWidth90_vs_SNR_q23.pdf}%\quad

@@

		Fig.~\ref{fig:TNT_chirpMassCIWidth90_vs_SNR_q23}, with the difference that  we

>>>>

\textbf{BH-BH Injection; BH-BH Templates}
\includegraphics[width=2\columnwidth]{plots/NN_chirpMassBias_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; BH-BH Templates}

@@

\textbf{NS-BH Injection; NS-BH Templates}

@@

	\textbf{BH-BH Injection; BH-BH Templates}
	\includegraphics[width=1.85\columnwidth]{plots/NN_chirpMassCIWidth90_vs_SNR_q23.pdf}\\ 
	\textbf{NS-BH Injection; BH-BH Templates}
	\includegraphics[width=1.85\columnwidth]{plots/TN_chirpMassCIWidth90_vs_SNR_q23.pdf}\\ 
	\textbf{NS-BH Injection; NS-BH Templates}
	\includegraphics[width=1.85\columnwidth]{plots/TT_chirpMassCIWidth90_vs_SNR_q23.pdf}%\quad

@@

\textbf{BH-BH Injection; BH-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/NN_EtaBias_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; BH-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/TN_EtaBias_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; NS-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/TT_EtaBias_vs_SNR_q23.pdf}%\quad

@@

\textbf{BH-BH Injection; BH-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/NN_EtaCIWidth90_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; BH-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/TN_EtaCIWidth90_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; NS-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/TT_EtaCIWidth90_vs_SNR_q23.pdf}%\quad

@@

  of the dimensionless mass-ratio $\eta$ here.}

@@

\textbf{BH-BH Injection; BH-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/NN_BHspinBias_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; BH-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/TN_BHspinBias_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; NS-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/TT_BHspinBias_vs_SNR_q23.pdf}%\quad

@@

\textbf{BH-BH Injection; BH-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/NN_BHspinCIWidth90_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; BH-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/TN_BHspinCIWidth90_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; NS-BH Templates}
\includegraphics[width=1.85\columnwidth]{plots/TT_BHspinCIWidth90_vs_SNR_q23.pdf}

@@

Fig.~\ref{fig:TNT_chirpMassCIWidth90_vs_SNR_q23}, with the difference that  
we consider the NS tidal parameter $\Lambda$ here.}
